Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling

### 2021-02-03 papers/intro_paper/acknowledgements.tex
small edit

The authors would like to thank everyone at the frontline of the Covid-19 pandemic. We would like to acknowledge the computing resources at the AEI and the LIGO Scientific Collaboration, specifically the Hypatia and CIT clusters. R.B. acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No. 792862, the European Union's H2020 ERC, Starting Grant agreement no.~DarkGRA--757480, and from the MIUR PRIN and FARE programmes (GW-NEXT, CUP:~B84I20000100001). We also acknowledge support from the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).

>>>>

The authors would like to thank everyone at the frontline of the Covid-19 pandemic. We would like to acknowledge the computing resources at the AEI and the LIGO Scientific Collaboration, specifically the Hypatia and CIT clusters. R.B. acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No. 792862, from the European Union's H2020 ERC, Starting Grant agreement no.~DarkGRA--757480, and from the MIUR PRIN and FARE programmes (GW-NEXT, CUP:~B84I20000100001). We also acknowledge support from the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
